Separation of an upwelling current bounding the Juan de Fuca Eddy, off Vancouver Island

### 2022-04-25 PW13Paper.tex
Author

\authors{Jody M. Klymak\affil{1} and Everyone }

% \affiliation{1}{First Affiliation}
% \affiliation{2}{Second Affiliation}
% \affiliation{3}{Third Affiliation}
% \affiliation{4}{Fourth Affiliation}
\affiliation{1}{School of Earth and Ocean Sciences and Department of Physcics \& Astronomy, University of Victoria, B.C.\ Canada}
%(repeat as many times as is necessary)

>>>>

\authors{Jody M. Klymak\affil{1}\affil{2} and Susan E. Allen\affil{3}\affil{4} and Others}

\affiliation{1}{School of Earth and Ocean Sciences, University of Victoria, BC, Canada}
\affiliation{2}{Department of Physcics \& Astronomy, University of Victoria, BC, Canada}
\affiliation{3}{Department of Earth, Ocean and Atmospheric Sciences, University of British Columbia, Vancouver, BC, Canada}
\affiliation{4}{Institute of Applied Mathematics, University of British Columbia, Vancouver, BC, Canada}
%(repeat as many times as is necessary)
